Reproducibility in plant pathology: where do we stand and a way forward

### 2021-10-14 analysis/paper/paper.Rmd
Clarify the prior distributions
Clarify modifying the 'adapt_delta()' and 'max_treedepth()'

Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.

@@

The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.

>>>>

Relatively flat priors were selected from a normal distribution with a mean of 0 and a standard deviation of 10 for all parameters.

@@

The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure a good model fit to the data and that the chains mixed well.
